---
title: "Functional connectivity of animal-dispersed plant communities depend on the
  interacting effects of network specialization and resource diversity"
author: "Anna Rebello Landim"
date: "2024-04"
output: html_document
---

This document provides the commented R-code to reproduce the simulations in the paper *Functional connectivity of animal-dispersed plant communities depend on the interacting effects of network specialization and resource diversity*.

{r setup, include=FALSE} knitr::opts_chunk\$set(warning = FALSE, echo = TRUE, fig.align='center', fig.width=6, fig.height=6, fig.show='hold', cache=TRUE, tidy=FALSE, tidy.opts=list(width.cutoff=80), size="small")

```{r}
library("vegan") 
library("Hmisc")
library("dplyr")
```

## Functions:

**Adapted and original functions from Donoso et al. (2017) and Sorensen et al. (2020):**

```{r}
## Adapted from Donoso et al. 2017

# Web to estimate fruit preference in the source patch (rowSums = 1):
makeweb_r <- function(specpar = 1, birdtraits, planttraits, nicheshape="normal"){

  fun_pref <- function(traitdif){
    if (nicheshape == "normal"){
      prefs <- dnorm(traitdif, mean = 0, sd=1/specpar)
    }
    if (nicheshape == "skewed"){
      prefs <- dlnorm(traitdif * specpar + exp (-1)) 
    }
    prefs
  }
  Nplant <- length(planttraits)
  Nbird <- length(birdtraits)
  web <- fun_pref(outer(planttraits, birdtraits, "-")*(-1)) 
  web
}

# Web to estimate preference to plants in target patch (colSums = 1):
makeweb_c <- function(specpar = 1, birdtraits, planttraits, nicheshape="normal"){
  
  fun_pref <- function(traitdif){
    if (nicheshape == "normal"){
      prefs <- dnorm(traitdif, mean = 0, sd=1/specpar)
    }
    if (nicheshape == "skewed"){
      prefs <- dlnorm(traitdif * specpar + exp (-1)) 
    }
    prefs
  }
  Nplant <- length(planttraits)
  Nbird <- length(birdtraits)
  web <- fun_pref(outer(planttraits, birdtraits, "-")*(-1)) 
  web
}

# Trait distributions:
get_skewtr <- function(myN, tr_meanlog = 2, tr_sdlog = 1.5){
  tr <- qlnorm(seq(0, 1, length.out = myN+2), tr_meanlog, tr_sdlog)[-c(1, myN+2)]
}

# Interaction network to define dispersal vectors:
# (uses preference web and interaction frequencies)
make_trueweb_r <- function(web_p, plantfreq, birdfreq){
  web_relfreq <- (plantfreq %*% t(birdfreq)) / mean(birdfreq)
  web_p * web_relfreq
}

# Interaction network to estimate attractiveness to target patch:
# (uses preference web and interaction frequencies) 
make_trueweb_c <- function(web_p, plantfreq){
  # Since we use this to estimate attractiveness for each bird, 
  # bird frequencies are always = 1
  web_p * plantfreq
}

## Original from Donoso et al. (2017):

# Function used to sample the interaction networks:
sampleweb <- function(web,obs=NULL,method='perplant'){
  if(method=='perplant') {
    if(length(obs)==1){obs <- rep(obs, nrow(web))}
    if(length(obs)!=nrow(web)){stop("length of obs neither 1 nor matching number of
                                           species")}
    sampledweb <- sapply(1:nrow(web), function(i) {
      web.i <- as.numeric(web[i,])
      table(sample(factor(1:length(web.i)), obs[i], prob = web.i, replace = TRUE))
    })
  }
  if(method=='percons') {
    if (length(obs)==1){obs <- rep(obs,ncol(web))}
    if (length(obs)!=ncol(web)){stop("length of obs neither 1 nor matching number of
                                           species")}
    sampledweb <- sapply(1:ncol(web), function(j) {
      web.j <- web[,j]
      table(sample(factor(1:length(web.j)),obs[j],prob=web.j,replace=TRUE)) 
    })
  }
  if(method=='perweb'){
    if (length(obs)!=1){stop("obs must have length 1 with method 'perweb'")}
    Nobs <- round(obs * ncol(web))
    sampledweb.vect <- sample(as.factor(1:length(web)), size=Nobs, prob=as.numeric(web),
                              replace=TRUE)
    sampledweb <- matrix(as.numeric(table(sampledweb.vect)), nrow=nrow(web)) 
  }
  if(method =='rarefy'){
    if(is.null(obs)) obs <- min(colSums(web)) 
    if(obs<1){stop("cannot rarefy to less than 1 observation")}
    sampledweb <- sapply(1:ncol(web), function(j) {
      web.j <- web[,j]
      24
      table(sample(rep(factor(1:length(web.j)),web.j),obs,replace=FALSE)) 
    })
  }
  dimnames(sampledweb) <- dimnames(web)
  sampledweb
}

## Original from Sorensen et al. 2020

# Function to convert a web interaction network back to a single frame (column of plant and column of birds) 
# one row for each interaction, equivalent function for the frame2web function in the bipartite package
web2frame <- function(x){
  newplant <- NULL
  newbird <- NULL
  new20 <- NULL
  for (i in 1:nrow(x)) {
    for (ii in 1:ncol(x)){
      newplant <- rep(rownames(x[i,]), each = x[i,ii])
      newbird <- rep(colnames(x[ii]), each = x[i,ii])
      new10 <- cbind(newplant,newbird)
      new20 <- rbind(new20, new10)
    }
    newplant <- NULL
    newbird <- NULL
    new10 <- NULL
  }
  return(new20)
}

# Function to create a single data frame with plants and birds traits:
matchbirdplanttraits <- function(simulatedframes, obs, N, birdtraits, planttraits) {
  bird.trait <- rep(NA, obs * N) 
  fruit.trait <- rep(NA, obs * N) 
  bird.trait2 <- rep(NA, obs * N)
  if(length(birdtraits) == 3){
    for(i in 1:nrow(simulatedframes)) {
      ti <- match(simulatedframes[i,2], birdtraits$birdnumber)
      z <- match(simulatedframes[i,1], planttraits$plantnumber)
      bird.trait[i] <- birdtraits[ti,1]
      fruit.trait[i] <- planttraits[z,1]
      bird.trait2[i] <- birdtraits[ti,3]
    }
    simulatedframes <- cbind(simulatedframes, bird.trait, fruit.trait, bird.trait2)
  } else {
    for(i in 1:nrow(simulatedframes)) {
      ti <- match(simulatedframes[i,2], birdtraits$birdnumber)
      z <- match(simulatedframes[i,1], planttraits$plantnumber)
      bird.trait[i] <- birdtraits[ti,1]
      fruit.trait[i] <- planttraits[z,1]
    }
    simulatedframes <- cbind(simulatedframes, bird.trait, fruit.trait)
  }}

# Simulation of dispersal distances:
dispsimulation <- function (x, obs, N) {
  dispdist <- rep(NA, obs * N) 
  for(i in 1:nrow(x)) {
    meanGPThour <- 4.5*x[i,3]^0.5 
    meanGPT <- meanGPThour*3600
    scalevalue <- 75311/meanGPT
    shapevalue <- meanGPT^2/75311
    GPT <- rgamma(1, shape = shapevalue, scale = scalevalue)
    meanspeed <- 15.7*x[i,3]^0.17
    speed <- rnorm(1, meanspeed, 2.078)  
    max_distance <- speed*GPT
    distance <- 0.002 * max_distance 
    if (is.nan (distance)){
      distance<-NA
    }
    dispdist[i] <- distance
  }
  x <- cbind(x, dispdist)
}
```

**New functions:**

```{r}
## Estimating probability of seed dispersal success:

distancefilter <- function(patches, Nplant, obs, simulatedframe){
  
  dist_filt <- array(dim = c(length(patches), obs, Nplant), dimnames = list(paste0("patch_", patches), paste0("event_", 1:obs), paste0("plant_", 1:Nplant)))
  
  for(p in 1:length(patches)){
    
    d <- patches[p]
    
    for(j in 1:Nplant){
      
      disp_dist <- t(matrix(simulatedframe[simulatedframe$newplant == j, "dispdist"]))
      
      for(i in 1:length(disp_dist)){
        if(disp_dist[i]-d < 0){
          disp_dist[i] <- 0
        } else {
          disp_dist[i] <- 1
        }
      }
      dist_filt[p,,j] <- disp_dist
    }
  }
  return(dist_filt)
}

## Estimating relative attractiveness of target patch:

# Random plant assembly

r_webs_rand <- function(specsparlevel, Nplant, Nbird, Nrep, rec_webs_p){
  alldata <- vector("list", length = length(specsparlevel))
  names(alldata) <- paste("Specialization.level", c(specsparlevel), sep="_")
  
  for(s in 1:length(specsparlevel)){
    specspar_data <- vector("list", length = Nplant+1)
    
    for(k in 1:(Nplant+1)){ 
      specspar_data[[k]] <- array(NA, dim = c((Nplant-k+1), Nbird, Nrep))
    }
    
    names(specspar_data) <- paste('Nplant.recipient',Nplant:0, sep='_')
    
    for(n in 1:Nrep){
      web.old <- rec_webs_p[[s]]
      
      seq.ran <- sample(rownames(rec_webs_p[[s]]))
      
      for(k in 1:(Nplant)){
        specspar_data[[k]][,,n] <- web.old
        web.old <- web.old[-which(rownames(web.old)==seq.ran[k]),, drop=FALSE]
      }
    }
    specspar_data[[(Nplant+1)]] <- array(0, dim = c(1, Nbird, Nrep))
    alldata[[s]] <- specspar_data
  }
  return(alldata)
}

# Relative attractiveness per plant richness in target patch: 

attractivenessfilter <- function(simulatedframes, source_webs_p, recipient_webs, specsparlevel, obs, Nplant, Nrep, Ncons, plant_freq){
  
  attrac_filt <- vector("list", length(specsparlevel))
  names(attrac_filt) <- paste("Specialization_level", c(specsparlevel), sep = "_")
  
  for(s in 1:length(specsparlevel)){
    
    attrac_filt_ww <- array(dim = c(length(recipient_webs[[s]]), obs, Nplant, Nrep), 
                            dimnames = list(paste0("re_p_comm_", 1:(length(recipient_webs[[s]]))), 
                                            paste0("event_", 1:obs), paste0("plant_", 1:Nplant),
                                            paste0("iteration_",1:Nrep)))
    
    for(w in 1:Nplant){
      
      rec <- colSums(recipient_webs[[s]][[w]])
      sourc_rec <- (colSums(plant_freq*source_webs_p[[s]]) + colSums(recipient_webs[[s]][[w]]))
      attrac <- as.data.frame(rec/sourc_rec)
      attrac$cons_id <- c(1:Ncons)
      row.names(attrac) <- NULL
      
      for(j in 1:Nplant){
        
        simulatedframes_s <- simulatedframes[[s]]
        attrac_plantcomm <- array(t(matrix(simulatedframes_s[simulatedframes_s$newplant == j, "newbird"])), dim = c(1, obs, Nrep))
        
        for(i in 1:obs){
          for(n in 1:Nrep){
            id <- match(attrac_plantcomm[,i,n], attrac$cons_id)
            attrac_plantcomm[,i,n] <- attrac[id, n]
          }
        }
        attrac_filt_ww[w,,j,] <- as.numeric(attrac_plantcomm)
      }
    }
    
    for(j in 1:Nplant){
      attrac_filt_ww[Nplant+1,,j,] <- array(0, dim = c(1,obs,n))
    }
    attrac_filt[[s]] <- attrac_filt_ww
  }
  return(attrac_filt)
}

## Combining distance and direction:

# For all species:
reach_prob_webs <- function(recipient_webs, specsparlevel, patches, obs, Nplant, Nrep,
                            filter_distance_webs, filter_attrac_webs){
  
  prob_webs <- vector("list", length(recipient_webs[[1]]))
  
  for(w in 1:length(recipient_webs[[1]])){
    
    probs_web_w <- vector("list", length(specsparlevel))
    
    for(s in 1:length(specsparlevel)){
      
      probs_s <- array(dim = c(length(patches),obs, Nplant, Nrep), 
                       dimnames = list(paste0("patch_", patches), 
                                       paste0("event_", 1:obs), 
                                       paste0("plant_", 1:Nplant),
                                       paste0("iteration_", 1:Nrep)))
      
      for(i in 1:Nplant){
        for(n in 1:Nrep){
          prob_plant_i <- sweep(filter_distance_webs[[s]][,,i], 2, filter_attrac_webs[[s]][w,,i,n], "*")
          
          probs_s[,,i,n] <- prob_plant_i
        }
      }
      probs_web_w[[s]] <- probs_s
    }
    names(probs_web_w) <- paste("Specialization_level", c(specsparlevel), sep = "_")
    prob_webs[[w]] <- probs_web_w  
  }
  names(prob_webs) <- paste("Plant_Rich", Nplant:0, sep = "_")
  return(prob_webs)
}

# Combining species result into community of seeds dispersed to target patches:
seeds_reaching_webs <- function(reach_prob_webs, specsparlevel, Nplant, Nrep, patches){
  
  n_seeds_webs <- vector("list", length(specsparlevel))
  
  for(s in 1:length(specsparlevel)){
    
    n_seeds <- array(NA, dim = c(length(patches), Nplant, Nrep),  
                     dimnames = list(paste0("Patch_", patches),
                                     paste0("Plant_",c(1:Nplant)), paste0("Iteration_", c(1:Nrep))))
    
    reach_prob <- reach_prob_webs[[s]]
    
    for(i in 1:Nplant){
      for(n in 1:Nrep){
        n_seeds_plant_i <- reach_prob[,,i,n]
        n_seeds_plant_i <- rowSums(n_seeds_plant_i)
        n_seeds[,i,n] <- n_seeds_plant_i 
      }
    }   
    n_seeds_webs[[s]] <- n_seeds
  }
  names(n_seeds_webs) <- paste("Specialization_level", c(specsparlevel), sep = "_")
  return(n_seeds_webs)
}

# Number and diversity of reaching seeds:
dispersal_dimensions <- function(Nplant, specsparlevel, Nrep, patches, n_seeds_reaching_webs, plant_trait, recipient_webs, plant_freq, obsperplant){
  Dispersed <- vector("list", length = (Nplant+1))
  
  for(w in 1:(Nplant+1)){
    
    Dispersed_webs <- vector("list", length = length(specsparlevel))
    
    for(s in 1:length(specsparlevel)){
      
      disp <- vector("list", length = Nrep)
      
      for (n in 1:Nrep){ 
        disp_it <- as.data.frame(c(patches))
        colnames(disp_it)[1] <- "Distance"
        disp_it$Spec.par.level <- as.factor(rep(specsparlevel[s], times = length(patches)))
        # Richness_recipient
        if(w==(Nplant+1)){
          disp_it$Rich_recipient <- rep((0), times = length(patches))
        } else {disp_it$Rich_recipient <- rep(as.numeric(c(Nplant:0)[w]), times = length(patches))}
        # Estimations
        disp_it$Abundance <- rowSums(n_seeds_reaching_webs[[w]][[s]][,,n]) 
        disp_it$Diversity <- exp(diversity(n_seeds_reaching_webs[[w]][[s]][,,n], index="shannon"))
        disp[[n]] <- disp_it  
      } 
      Dispersed_webs[[s]] <- bind_rows(disp)
    }
    Dispersed[[w]] <- bind_rows(Dispersed_webs)
  }
  return(bind_rows(Dispersed))
}
```

## Simulated plant and bird communities:

We used empirical trait data from plant and bird communities in Manú Biosphere Reserve, Peru.

```{r}
# Empirical plant community:
Plants <- read.csv("Manu_plant.community.csv")

# Empirical bird community:
Birds <- read.csv("Manu_bird.community.csv")
```

This data was used to simulate seed-dispersal networks for a community composed of 60 bird and 50 plant species.

**(I): Generate the simulated species pool**

```{r}
Nbird <- 60
Nplant <- 50
```

**(II): Draw trait values**

We use mean and standard deviation of the empirical communities to create trait distributions of our simulated communities.

```{r}

### Get mean and standard deviation from empirical communities:

## Traits related to birds' fruit preferences:

# Fruit width
p_fw_meanlog <- mean(log(Plants$Fruit.D1.mm))
p_fw_sdlog <- sd(log(Plants$Fruit.D1.mm))

# Bill width
b_bw_meanlog <- mean(log(Birds$Bill.width.mm)) 
b_bw_sdlog <- sd(log(Birds$Bill.width.mm))

## Traits related to primarily used forest strat:

# Height
p_h_meanlog <- mean(log(Plants$Plant.height.m))
p_h_sdlog <- sd(log(Plants$Plant.height.m))

# Wing Pointdness
b_wp_meanlog <- mean(log(Birds$Kipp_index))
b_wp_sdlog <- sd(log(Birds$Kipp_index))

### Estimate distributions with mean and standard deviation from the empirical communities:

## Traits related to birds' fruit preferences:

# Fruit width
fit_p_fw <- get_skewtr(Nplant, p_fw_meanlog, p_fw_sdlog) 

# Bill width
fit_b_bw <- get_skewtr(Nbird, b_bw_meanlog, b_bw_sdlog)

## Traits related to primarily used forest strat:

# Height
fit_p_h <- get_skewtr(Nplant, p_h_meanlog, p_h_sdlog) 

# Wing Pointdness
fit_b_wp <- get_skewtr(Nbird, b_wp_meanlog, b_wp_sdlog)
```

**(III) Estimate interaction frequencies:**

We used fruit size and avian body mass to estimate interaction frequencies.

```{r}

# Plants: We assume the relationship: y=1/x
p_v <- Plants$Fruit.length.mm * Plants$Fruit.D1.mm * Plants$Fruit.D2.mm

p_v_meanlog <- mean(log(na.omit(p_v)^(1/3)))
p_v_sdlog <- sd(log(na.omit(p_v)^(1/3)))
fit_p_v <- get_skewtr(Nplant, p_v_meanlog, p_v_sdlog) 

YES_pl_freq <- (1/fit_p_v)/mean((1/fit_p_v)) 

# Birds: We assume a negative relationship: y=(1/x)+b, where b is thee undercompensation parameter set to the 10% of the maximum value of 1/x
b_bm_meanlog <- mean(log(Birds$Bodymass.g^(1/3))) 
b_bm_sdlog <- sd(log(Birds$Bodymass.g^(1/3))) 
fit_b_bm <- (get_skewtr(Nbird, b_bm_meanlog, b_bm_sdlog))

v10 <- max(1/fit_b_bm)/10
YES_bird_freq <- ((1/fit_b_bm) + v10)/mean((1/fit_b_bm)+v10) 
```

## Interaction networks:

Using the trait values and interaction frequencies from our simulated plant and bird communities, we built seed-dispersal networks to define the vectors of seed dispersal in the source patch. We varied network specialization levels to test its effect on plant functional connectivity.

**(IV) Generate the seed dispersal networks:**

```{r}
# Set specialization parameter levels
networkreplicates <- 1
specsparlevel <- c(
  rep(1.5, networkreplicates) # H2' = 0.1587484
  , 
  rep(5, networkreplicates) # 0.308189
  ,
  rep(10, networkreplicates) # 0.4556191
  ,
  rep(20, networkreplicates) # 0.6532462
)

# Interaction probabilities according to trait matching (bill x fruit width and wing pointedness and plant height)
webs_p_2 <- vector("list", length(specsparlevel))
webs_p_t1 <- lapply(specsparlevel, makeweb_r, birdtraits = as.vector(decostand(fit_b_bw, "range")), planttraits = as.vector(decostand(fit_p_fw, "range")),
                    nicheshape = "skewed")
webs_p_t2 <- lapply(specsparlevel, makeweb_r, birdtraits = as.vector(decostand(fit_b_wp, "range")), planttraits = as.vector(decostand(fit_p_h, "range")),
                    nicheshape = "normal")
for(i in 1:length(specsparlevel)){
  t1t2 <- webs_p_t1[[i]]*webs_p_t2[[i]]
  t1t2 <- t1t2 / matrix(rowSums(t1t2), nrow = Nplant, ncol = Nbird)
  webs_p_2[[i]] <- t1t2
}

# Interaction networks built using interaction frequencies and interaction probabilites:
webs_2 <- lapply(webs_p_2, make_trueweb_r, birdfreq=YES_bird_freq, plantfreq=YES_pl_freq)
funct <- function(x){x/matrix(rowSums(x)/YES_pl_freq, nrow=Nplant, ncol=Nbird)}
webs_2 <- lapply(webs_2, funct)
```

**(V) Sample the seed-dispersal networks:**

Using the simulated seed-dispersal networks, we sampled 100 seed-dispersal events (observations) per plant species in the source patch.

```{r}
obsperplant <- 100 

webs_largesamp_2 <- lapply(webs_2, sampleweb, obs=obsperplant, method='perplant')
webs_largesamp_2 <- lapply(webs_largesamp_2, t)
for(i in 1:length(webs_largesamp_2)){
  colnames(webs_largesamp_2[[i]]) <- c(1:Nbird)
  rownames(webs_largesamp_2[[i]]) <- c(1:Nplant)
  webs_largesamp_2[[i]] <- as.data.frame(webs_largesamp_2[[i]]) 
}
```

## Seed dispersal distances

We estimated the distance of seed dispersal events using bird body mass. Seed-dispersal success was estimated based on the difference between seed-dispersal distance and between-patch distance.

**(VI) Estimate dispersal distances for each event**

```{r}
# Bird traits (for data frame)
b_bm_meanlog_dist <- mean(log(Birds$Bodymass.g)) 
b_bm_sdlog_dist <- sd(log(Birds$Bodymass.g)) 
fit_b_bm_dist <- (get_skewtr(Nbird, b_bm_meanlog_dist, b_bm_sdlog_dist))/1000

fit_b_bm_df <- as.data.frame(fit_b_bm_dist)
fit_b_bw_df <- as.data.frame(fit_b_bw)

birdtrait <- as.data.frame(cbind(fit_b_bm_df, as.character(c(1:Nbird)), fit_b_bw_df))
colnames(birdtrait)[2] <- "birdnumber"

# Plant trait (for data frame)
fit_p_fw_df <- as.data.frame(fit_p_fw)

planttrait <- as.data.frame(cbind(fit_p_fw_df, as.character(c(1:Nplant))))
colnames(planttrait)[2] <- "plantnumber"

# Creating data frames with simulated dispersal distances of all seed-dispersal events of each plant species in the source patch
simulatedframes_2 <- lapply(webs_largesamp_2, web2frame)
simulatedframes_2 <- lapply(simulatedframes_2, as.data.frame)
simulatedframes_2 <- lapply(simulatedframes_2, matchbirdplanttraits, obs = obsperplant, 
                            N = Nplant, birdtraits = birdtrait, planttraits = planttrait) 
simulatedframes_2 <- lapply(simulatedframes_2, dispsimulation, obs = obsperplant, N = Nplant)
```

**(VII) Calculate reacheable patches**

```{r}
# Simulated between-patch distances
patches <- c(seq(from = 0, to = 600, by = 10))

# Calculate difference between seed-dispersal and between-patch distances to calculate reacheable patches
filter_distance_webs_2 <- lapply(simulatedframes_2, distancefilter, patches = patches,
                                 Nplant = Nplant, obs = obsperplant)
```

## Direction: target patches

Here we simulate plant community assembly at the target patch, with iterations sequentially increasing plant richnes form 0 to 50 plant species in the target patch. Then, we estimate the relative attractivness of the target patch at each step along the assembly sequence. The relative attractivness value was used to estimate the probability of bird movement direction to the target patch.

**(VIII) Make assembly sequences in the target patch**

```{r}

# Setting number of iterations
Nrep <- 100 

# Interaction probabilities between seed dispersers and plants in the target patch (i.e., estimating fruit preferences)
rec_webs_p_2 <- vector("list", length = length(specsparlevel))

for(s in 1:length(specsparlevel)){
  rec_webs_p_t1 <- makeweb_c(specpar=specsparlevel[[s]], birdtraits = as.vector(decostand(fit_b_bw, "range")), 
                             planttraits = as.vector(decostand(fit_p_fw, "range")),
                             nicheshape = "skewed")
  
  rec_webs_p_t2 <- makeweb_c(specpar=specsparlevel[[s]], birdtraits = as.vector(decostand(fit_b_wp, "range")), 
                             planttraits = as.vector(decostand(fit_p_h, "range")),
                             nicheshape = "normal")
  
  t1t2 <- (rec_webs_p_t1*rec_webs_p_t2)
  t1t2 <- t1t2 / matrix(rowSums(t1t2), nrow = Nplant, ncol = Nbird)
  true_t1t2 <- make_trueweb_c(t1t2, YES_pl_freq)
  
  rec_webs_p_2[[s]] <- true_t1t2
  
}

for(i in 1:length(specsparlevel)) { 
  dimnames(rec_webs_p_2[[i]]) <- list(paste('p',1:Nplant,sep=''),paste('b',1:Nbird,sep='')) 
}

# Simulating plant assemblies at target patch

rec_webs_2 <- r_webs_rand(specsparlevel, Nplant, Nbird, Nrep, rec_webs_p_2)
```

**(IX) Calculate relative attractiveness**

```{r}
filter_attrac_webs_2 <- attractivenessfilter(simulatedframes=simulatedframes_2, 
                                                  source_webs_p = webs_p_2,
                                                  recipient_webs=rec_webs_2, 
                                                  specsparlevel=specsparlevel, 
                                                  obs=obsperplant, 
                                                  Nplant=Nplant, 
                                                  Nrep = Nrep,
                                                  Ncons=Nbird, plant_freq = YES_pl_freq)
```

## Community-level plant functional connectivity

We integrate the results from distance and direction by multiplying the resulting matrices from both analyses. In that way, if a seed is able to reach a certain patch (seed-dispersal distance \>= between-patch distance), the probability of the animal seed disperser moving in direction of a target patch is defined by the target patch's relative attractiveness. Based on these results, we quantified both the number and diversity of seeds arriving at the target patch.

**(X) Estimate number of seeds that reach the target patch**

```{r}
# Probability of seeds reaching the target patch per seed-dispersal event
seeds_reach_prob_webs_2 <- reach_prob_webs(recipient_webs = rec_webs_2, specsparlevel = specsparlevel, patches = patches, obs = obsperplant, Nplant = Nplant, Nrep = Nrep,
                                           filter_distance_webs = filter_distance_webs_2, filter_attrac_webs = filter_attrac_webs_2)

# Total number of seeds reaching the target patch (sum over the probabilities per species)
n_seeds_reaching_webs_2 <- lapply(seeds_reach_prob_webs_2, seeds_reaching_webs,
                                  specsparlevel = specsparlevel, Nplant=Nplant, 
                                  Nrep=Nrep, patches=patches)

# Applying a threshold for the number of seeds that reach the recipient patch.
# *If the total number of seeds of a certain species reaching the target patch is below 1, we set the number of seeds to 0, indicating that no seeds from that plant species reached the target patch in that scenario of between-patch distance and plant richness of the target patch.

t_1 <- vector("list", length = length(n_seeds_reaching_webs_2))
for(r in 1:length(n_seeds_reaching_webs_2)){
  s_1 <- vector("list", length(specsparlevel))
  for(s in 1:length(specsparlevel)){
    s_1[[s]] <- ifelse(n_seeds_reaching_webs_2[[r]][[s]] < 1.0, 0, n_seeds_reaching_webs_2[[r]][[s]])
  }
  names(s_1) <- paste("Specialization_level", c(specsparlevel), sep = "_")
  t_1[[r]] <- s_1
}
names(t_1) <- paste("Plant_Rich", Nplant:0, sep = "_")
```

**(XI) Estimate plant diversity in the target patch**

```{r}
disp_dim_2 <- dispersal_dimensions(Nplant, specsparlevel, Nrep, patches, t_1, fit_p_fw, rec_webs_2, YES_pl_freq, obsperplant)
```

# Plots

```{r}
# Mean and confidence intervals
CI_2 <- disp_dim_2 %>%
  dplyr::group_by(Spec.par.level, Distance, Rich_recipient) %>%
  dplyr::summarise(
    mean_diversity = mean(Diversity),
    mean_abundance = mean(Abundance),
    low.q_diversity = quantile(Diversity, probs = 0.025),
    low.q_abundance = quantile(Abundance, probs = 0.025),
    high.q_diversity = quantile(Diversity, probs = 0.975),
    high.q_abundance = quantile(Abundance, probs = 0.975))

library("ggplot2")

CI_2$Spec.par.level <- as.factor(CI_2$Spec.par.level)

# Number of seeds

ggplot(CI_2[CI_2$Distance==10,], # Here you can set the distance you want to plot
       aes(log(Rich_recipient), mean_abundance, colour = Spec.par.level)) +
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = low.q_abundance, ymax = high.q_abundance, fill = Spec.par.level), linetype = 0, alpha = 0.2) +
  geom_segment(aes(x = -Inf, y = 500, xend = log(50), yend = 500), linetype = "dotted", linewidth = .9, colour = "red") +
  scale_color_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4", "#6A4C93")) +  
  scale_fill_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4", "#6A4C93")) + 
  scale_y_continuous(limits = c(0, 2500), breaks = c(0, 500, 1000, 1500, 2000, 2500), labels = c(0, 500, 1000, 1500, 2000, 2500)) + # 10 and 50m
  # scale_y_continuous(limits = c(0, 800), breaks = c(0, seq(from=100, to=800, by=100)), labels = c(0,  seq(from=100, to=800, by=100))) + # 100 and 250m
  scale_x_continuous(breaks = c(log(c(1, 2:6, 8, 15, 25, 50))), labels = c(1, 2:6, 8, 15, 25, 50)) +
  guides(colour = "none") +
  theme_classic() +
  theme(axis.title = element_blank(), axis.text = element_text(size=12), legend.position = "none",
        axis.title.x = element_blank(), axis.title.y = element_blank(),  plot.margin = margin(t = 0.5, b = 1.5, l = 1.5, r = 0.5, unit = "lines"))


# Seed diversity
ggplot(CI_2[CI_2$Distance==100,] # Here you can set the distance you want to plot
       , aes(log(Rich_recipient), mean_diversity, colour = Spec.par.level)) +
  geom_line(linewidth = 1) +
  geom_ribbon(aes(ymin = low.q_diversity, ymax = high.q_diversity, fill = Spec.par.level), linetype = 0, alpha = 0.2) +
  geom_segment(aes(x = -Inf, y = 10, xend = log(50), yend = 10), linetype = "dotted", linewidth = .9, colour = "red") +
  scale_color_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4")) +  
  scale_fill_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4")) + 
  ylim(c(0,50)) +
  scale_x_continuous(breaks = c(log(c(1, 2:6, 8, 15, 25, 50))), labels = c(1, 2:6, 8, 15, 25, 50)) +
  guides(colour = "none") +
  theme_classic() +
  theme(axis.title = element_blank(), axis.text = element_text(size=12), legend.position = "none",
        axis.title.x = element_blank(), axis.title.y = element_blank())

## Smoothing for 250m:
CI_2.2 <- CI_2 %>%
  mutate(Rich_recipient_log = log(Rich_recipient+1))

filtered_data <- CI_2.2 %>%
  filter(Distance == 250 & Spec.par.level != 0.5)

loess_span <- 4  

data_to_smooth <- filtered_data %>% filter(Rich_recipient >= 20)
data_no_smooth <- filtered_data %>% filter(Rich_recipient < 20) 

smoothed_means <- data_to_smooth %>%
  group_by(Spec.par.level) %>%
  do({
    model <- loess(mean_diversity ~ Rich_recipient_log, data = ., span = loess_span)
    data.frame(Rich_recipient_log = .$Rich_recipient_log, pred = predict(model, se = FALSE))
  })

smoothed_confidence <- data_to_smooth %>%
  group_by(Spec.par.level) %>%
  do({
    model_lower <- loess(low.q_diversity ~ Rich_recipient_log, data = ., span = loess_span)
    model_upper <- loess(high.q_diversity ~ Rich_recipient_log, data = ., span = loess_span)
    data.frame(Rich_recipient_log = .$Rich_recipient_log, lower = predict(model_lower), upper = predict(model_upper))
  })

combined_means <- rbind(smoothed_means, data_no_smooth %>% mutate(pred = mean_diversity))
combined_confidence <- rbind(smoothed_confidence, data_no_smooth %>% mutate(lower = low.q_diversity, upper = high.q_diversity))

combined_means <- combined_means %>% mutate(un_rr = exp(Rich_recipient_log) - 1)
combined_confidence <- combined_confidence %>% mutate(un_rr = exp(Rich_recipient_log) - 1)

ggplot() +
  geom_line(data = combined_means, linewidth = 1, aes(x = log(un_rr), y = pred, colour = Spec.par.level)) +
  geom_ribbon(data = combined_confidence, aes(x = log(un_rr), ymin = lower-.1, ymax = upper, fill = Spec.par.level), alpha = 0.2) +
  geom_segment(aes(x = -Inf, y = 10, xend = log(50), yend = 10), linetype = "dotted", linewidth = .9, colour = "red") +
  scale_color_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4")) +  
  scale_fill_manual(values = c("#FF595E", "#FFCA3A", "#8AC926", "#1982C4")) + 
  scale_y_continuous(limits = c(0, 10), breaks = c(0:10), labels = c(0:10)) + 
  scale_x_continuous(breaks = c(log(c(1, 2:6, 8, 15, 25, 50))), labels = c(1, 2:6, 8, 15, 25, 50)) +
  guides(colour = "none") +
  theme_classic() +
  theme(axis.title = element_blank(), axis.text = element_text(size=12), legend.position = "none",
        axis.title.x = element_blank(), axis.title.y = element_blank())
```
